\begin{thebibliography}{999}
\addcontentsline{toc}{chapter}{\numberline{}Bibliografía}

\bibitem{aden96}
Adenso, B., {\it Optimización Heurística y Redes Neuronales}, Paraninfo, 1996

\bibitem{EJB}
D. Alur, J. Crupi, D. Malks, {\it Core J2EE Patterns, second edition}, Prentice Hall, 2003

\bibitem{bell03}
Bellas Bouza, F. J., {\it MDB: Mecanismo congnitivo darwinista para agentes autónomos}, Tesis Doctoral, Universidade da Coruña, 2003.

\bibitem{bell05}
F. Bellas, J.A. Becerra,  R. J. Duro, {\it Induced behavior in a real agent using the Multilevel Darwinist Brain}

\bibitem{brad97}
Bradshaw, J., \emph{Software Agents}, The MIT Press, 1997.

\bibitem{cao02}
Ricardo Cao Abad, {\it Introducción a la Simulación y a la Teoría de Colas}, netbiblo, 2002.

\bibitem{corr}
Jan M. Correa and Alba C. Melo, {\it Using a Classifier System to Improve Dynamic Load Balancing}.

\bibitem{etzi94}
Etzioni, O., {\it A Softbot-Based Interface to the Internet}, Communications of the ACM, pp 72-76, 1994.

\bibitem{fran99}
H. Franke, J. Jann, J. Moreira, P. Pattnaik and M. Jette, 
{\it An Evaluation of Parallel Job Scheduling for ASCI Blue-Pacific}, 
Proceedings of SC'99, pp 11-18, ACM Press and IEEE Computer Society Press, Portland, Oregon, 1999.

\bibitem{feit97}
D. G. Feitelson and M. A. Jette, 
{\it Improved Utilization and Responsiveness with Gang Scheduling}, 
Proceedings of 3rd Workshop on Job Scheduling Strategies for Parallel Processing, 
vol 1291, pp 238-262, Springer Verlag, 1997.

\bibitem{feit98}
D. G. Feitelson and A. Weil, 
{\it Utilization and Predictability in Scheduling the IBM SP2 with Backfilling}, 
Proceedings of the 1st Merged International Parallel Processing Symposium and Symposium on Parallel 
and Distributed Processing (IPPS/SPDP-98), pp 542-547, IEEE Computer Society, Los Alamitos, marzo 1998.

\bibitem{feit99}
D. G. Feitelson and M. Naaman, {\it Self-Tuning Systems}, 
IEEE Software n.16(2), pp 52-60, abril / mayo 1999.

\bibitem{fran96}
Franklin S., Graesser A., {\it Is it an Agent, or just a Program? A taxonomy for
Autonomous Agents}, Procs. 3rd. International Workshop on Agent Theories, Architectures and Languages, pp 21-35, 1996.

\bibitem{gamm95}
E. Gamma, R. Helm, R. Johnson, J, Vlissides, {\it Patrones de diseño}, Addison-Wesley, 1995.

\bibitem{gold87}
Goldberg, D. E., 
{\it Simple Genetic Algorithms and the Minimal, Deceptive Problem}, Genetic Algorithms and Simulated Annealing, L. Davis (Ed.) (San Mateo, California), pp. 74-88, 1987.

\bibitem{holl75}
Holland, J., {\it Adaptation in Natural and Artificial Systems}, 
University of Michingan Press, Ann Arbor, 1975.

\bibitem{maes90}
Maes, P., {\it Designing Autonomous Agents: Theory and Practice from Biology to
Engineering and Back}, MIT Press, 1990.

\bibitem{mar99}
Marín, J., Solé, R. V., {\it Macroevolutionary Algorithms: A New Optimization
Method en Fitness Landscapes}, IEEE Transactions on Evolutionary 
Computation 3(4):272-286, 1999

\bibitem{mccul43}
McCulloch, W. S. and Pitts, W., 
{\it A Logical Calculus of Ideas Inmanent in Nervous Activity}. Bull. Math. Biophys. 5, pp. 115-133, 1943.

\bibitem{more99}
J. Moreira, H. Franke, W. Chan and L. L. Fong, 
{\it A Gang-Scheduling System for ASCI Blue-Pacific}, 
Proceedings of the 7th International Conference in High-Performance Computing 
and Networking (HPCN'99), Lecture Notes in Computer Science, Vol. 1593, pp 831-940, Springer, 1999.

\bibitem{mual00}
A. Mu'alem and D. G. Feitelson, 
{\it Utilization, Predictability, Workloads and User Runtime Estimates in 
Scheduling the IBM SP2 with Backfilling}, 
Technical Report 2000-33, Institute of Computer Science, 
Hebrew University, Jerusalem, julio 2000.

\bibitem{nwan96}
Nwana, H., {\it Software Agents: An Overview}, Knowledge Engineering Review, vol
11, pp 1-40, 1996.

\bibitem{rech65}
Rechenberg, I., {\it Cybernetic Solution Path of an Experimental Problem},
 Library Translation 1122, Royal Aircraft Establishment, Farnborough, UK, 1965. 

\bibitem{robin02}
Neil Robinson, {\it Evolutionary Optimization of Market-Based 
Control Systems for Resource Allocation in Compute Farms}, 
HPL-2002-84, HP Laboratories Bristol, octubre 2002.

\bibitem{schw75}
Schwefel, H.P., {\it Evolutionsstrategie und Numerische Optimierung}, 
Ph. D. Thesis, Technische Universität Berlin, 1975.

\bibitem{skov96}
J. Skovira, W. Chan, H. Zhou and D. Lifka, 
{\it The EASY ? LoadLeveler API Project}, 
Proceedings of 2nd Workshop on Job Scheduling Strategies for Parallel Processing, 
vol 1162, pp 41-47, Springer Verlag, 1996.

\bibitem{streit01}
A. Streit, {\it On Job Scheduling for HPC-Clusters and the dynP Scheduler}, Proceedings of the 8th International Conference on High Performance Computing (HiPC 2001), Lecture Notes in Computer Science, vol 2228, pp 58-67, Springer, diciembre, 2001.

\bibitem{streit02}
A. Streit, {\it The Self-Tuning dynP Job-Scheduler}, Proceedings of the 11th International Heterogenous Computing Workshop (HCW) at IPDPS 2002, Lecture Notes in Computer Science, 2002.

\bibitem{sgeadmin}
Sun Microsystems, Inc.,
{\it N1 Grid Engine Administration Guide}, junio, 2004

\bibitem{talb99}
D. Talby and D. G. Feitelson, 
{\it Suporting Priorities and Improving Utilization of the IBM SP2 Scheduler Using Slack-Based Backfilling}, 
Technical Report 98-13, Hebrew University, Jerusalem, abril 1999.

\bibitem{whit89} 
Whitley D., 
{\it The GENITOR Algorithm and Selection Pressure: Why Rank-based Allocation of Reproductive Trials is Best.}, Proc. 3rd Int. Conf. on Genetic Algorithms pp 116-121 (Fairfax), J. D. Schaffer (Ed.) (San Mateo), 1989.

\bibitem{wool02}
M. Wooldridge, {\it An Introduction to MultiAgent Systems}, Wiley, 2002.

\bibitem{yao93}
Yao, X., {\it A Review of Evolutionary Artificial Neural Networks}, International Journal of Intelligent Systems, 8(4), pp 539-567, 1993.

\bibitem{zhan00}
Y. Zhang, H. Franke, J. E. Moreira and A. Sivasubramaniam, 
{\it Improving Parallel Job Scheduling by Combining Using Gang-Scheduling and 
Backfilling Techniques}, 
Proceedings of 14th Intenational Conference on Parallel and Distributed Processing Symposium (IPDPS-00), pp 133-144, Springer Verlag, 2000.

\bibitem{zhan01}
Y. Zhang, H. Franke, J. E. Moreira and A. Sivasubramaniam, 
{\it An Integrated Approach to Parallel Scheduling Using Gang-Scheduling, Backfilling and Migration}, 
Proceedings of 7th Workshop on Job Scheduling Strategies for Parallel Processing, 
vol 2221, pp 133-158, Springer Verlag, 2001.

\bibitem{ting03}
Tingshao Zhu, Russ Greiner, Gerald Häubl, {\it Learning a Model of a Web User's Interests}, Lecture Notes in Computer Science, volume 2702, 2003, pp. 65-75, 2003.

\bibitem{amazon}
{\it http://www.amazon.com/}, Amazon.com: Online shopping for electronics, apparel, music, books, DVDs \& more, último
acceso: 29 de junio de 2005.

\bibitem{cesga}
{\it http://www.cesga.es/}, CESGA, Centro de supercomputación de Galicia, último acceso: 26 de junio de 2005.

\bibitem{cesgasvg}
{\it http://www.cesga.es/ga/CalcIntensivo/SVG.html/}, CESGA, Centro de supercomputación de Galicia, 
último acceso: 18 de junio de 2005.

\bibitem{gridengine}
{\it http://gridengine.sunsource.net/}, gridengine: Home, último acceso: 26 de junio de 2005.

\bibitem{lsf}
{\it http://www.platform.com/}, Platform Computing - Accelerating Intelligence - Grid Computing, último acceso: 26 de junio de 2005.

\bibitem{maui}
{\it http://www.clusterresources.com/products/maui/}, Maui Cluster Scheduler, último acceso: 26 de junio de 2005.

\bibitem{myyahoo}
{\it http://es.my.yahoo.com/}, Mi Yahoo!, último acceso: 26 de junio de 2005.

\bibitem{openbps}
{\it http://www.openpbs.org/}, OpenPBS, último acceso: 26 de junio de 2005.

\bibitem{pbspro}
{\it http://www.pbspro.com/}, PBS Professional 7.0, último acceso: 26 de junio de 2005.

\bibitem{sge}
{\it http://www.sun.com/software/gridware/}, Sun N1 Grid Engine 6, último acceso: 26 de junio de 2005.
\end{thebibliography}

\cleardoublepage

\addcontentsline{toc}{chapter}{\numberline{}Glosario}
\printglossary


\cleardoublepage
\addcontentsline{toc}{chapter}{\numberline{}Índices de figuras y tablas}
\listoffigures
\cleardoublepage
\listoftables



